\documentclass[11pt]{article}
\usepackage[margin = 1in]{geometry}

\usepackage{amssymb}
\usepackage{afterpage}
\usepackage{array}
\usepackage{url}
\usepackage{natbib}
\usepackage[capposition=top]{floatrow}

\input{"paper_header"}
\graphicspath{{"figures/"}}

\renewenvironment{abstract}
 {\small
  \begin{center}
  \bfseries \abstractname\vspace{-.5em}\vspace{0pt}
  \end{center}
  \list{}{
    \setlength{\leftmargin}{35mm}
    \setlength{\rightmargin}{\leftmargin}%
  }
  \item\relax}
 {\endlist}

 \usepackage[dvipsnames]{xcolor}
 \usepackage{adjustbox}

%--------------------------------------------------------------
% Misc formatting
%--------------------------------------------------------------

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\violet}[1]{\textcolor{violet}{#1}}
\newcommand{\var}[1]{\textcolor{internationalkleinblue}{\texttt{#1}}}
\newcommand{\zvar}[1]{\textcolor{dgreen}{\texttt{#1}}}

% COMMENT OUT TO MAKE BLACK
%\definecolor{red}{cmyk}{0,0,0,1}
%\definecolor{blue}{cmyk}{0,0,0,1}
%\definecolor{orange}{cmyk}{0,0,0,1}
%\definecolor{violet}{cmyk}{0,0,0,1}

\usepackage{times}
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault}
\doublespacing
\emergencystretch 3em




%--------------------------------------------------------------
% Information
%--------------------------------------------------------------

\newcommand{\titletext}{Harnessing Social Media Influencers (or Simply Using Ads?)}

\newcommand{\authors}{
	Antonella Bandiera\thanks{Assistant Professor, Department of Political Science, ITAM. antonella.bandiera@itam.mx.} \and
    Shelley Liu\footnote{Assistant Professor, Sanford School of Public Policy, Duke University. Email: \href{mailto:shelley.liu@duke.edu}{shelleyxliu@berkeley.edu}} \and 
	Jeremy Bowles\thanks{Assistant Professor, Department of Political Science and School of Public Policy, University College London. jeremy.bowles@ucl.ac.uk.} \and 
	Horacio Larreguy\thanks{Associate Professor, Economics and Political Science, ITAM. horacio.larreguy@itam.mx.} \and
	John Marshall\thanks{Associate Professor, Department of Political Science, Columbia University. jm4401@columbia.edu.} \and
    Eduardo Zago\thanks{PhD Student in Politics, NYU. ez2490@nyu.edu .} \and 
    Joaquín Barrutia\thanks{PhD Student in Economics, Emory University. joaquin.barrutia.alvarez@emory.com.}, 
 
}

\newcommand{\acknowledgements}{}


\newcommand{\abstracttext}{%
	\begin{abstract}
		\noindent 

  
		\\ \vspace{2em}
		
	\end{abstract}
}

\newcommand{\Nintensive}{N = 170,547. }

\newcommand{\Nextensive}{N = 96,390. }

\newcommand{\IntensiveTreatment}{The treatment variable is the number of treated influencers each user follows. We use total influencers followed, treatment and control, fixed effects. Standard errors are estimated using bootstrap repetitions of 1000 different treatment assignments. }

\newcommand{\ExtensiveTreatment}{The treatment variable is a dummy which is 1 if a user follows a treatment influencer, 0 in other case. We use influencer-block fixed effects. Standard errors are estimated using bootstrap repetitions of 1000 different treatment assignments. }

\newcommand{\TreatmentAds}{The treatment variable is 1 for users that were in the list for which Africa Check's advertisement campaign was directed to. We use stratification-block fixed effects. Robust standard errors are estimated. }

\newcommand{\VerifiabilityNote}{This figure illustrates the dynamic estimates of the intervention's impact, depicting the number of Tweets (posts and RTs) generated by users, the portion of these Tweets identified as verifiable and non-verifiable by our BERT model, and the breakdown of predicted verifiable Tweets into true and false categories. All dependent variables are winsorized at the 95\% level.  }

\newcommand{\VerAdsNote}{This figure illustrates the dynamic estimates of the Twitter (X) Ads intervention's impact, depicting the number of Tweets (posts and RTs) generated by users, the portion of these Tweets identified as verifiable and non-verifiable by our BERT model, and the breakdown of predicted verifiable Tweets into true and false categories. All dependent variables are winsorized at the 95\% level. The analysis focuses on followers from batches 1 and 2 who made at least one post during their respective baseline periods. }


\newcommand{\SentimentBertNote}{This figure illustrates the dynamic estimates of the intervention's impact, depicting the total number, as well as the positive, neutral and negative Tweets (posts and RTs) that refer to COVID or COVID vaccines. We trained and used a BERT model for sentiment analysis prediction. }

\newcommand{\SentimentVADERNote}{This figure illustrates the dynamic estimates of the intervention's impact, depicting the total number, as well as the positive, neutral and negative Tweets (posts and shares) that refer to COVID or COVID vaccines. We used VADER for sentiment analysis prediction. }


\newcommand{\URLsNote}{This figure illustrates the dynamic estimates of the intervention's impact, showing the number of total URLs shared by users (Total URLs), the portion of these URLs identified as coming from a news source (Total News), and the breakdown of these news sources that are reliable and non-reliable (Reliable and Non-Reliable News), labeled by Africa Check and using NewsGuard. We also include the total number of URLs that contain information such as newsites, articles and blog posts (Other Info.) and URLs that are from other websites such as gambling sites, etc (Not Information). Finally, we include the total number of URLs that lead into a fact-checking organization (Fact-Checks). }

\newcommand{\VerIntNote}{This figure illustrates the dynamic estimates of the intervention's impact, depicting the number of interactions from posts generated by users, the portion of these interactions coming from posts identified as verifiable and non-verifiable by our BERT model, and the breakdown of these predicted verifiable posts into true and false categories. }

\newcommand{\SentIntNote}{This figure illustrates the dynamic estimates of the intervention's impact, depicting the number of interactions from posts generated by users that refer to COVID, the portion of these interactions coming from posts predicted as positive, negative and neutral. For the sentiment analysis prediction we used a BERT model. }

\newcommand{\RTNote}{This figure illustrates the dynamic estimates of the intervention's impact, depicting the number of ReTweets from the SMIs' and Africa Check's accounts that each user did. }


\begin{document}

%--------------------------------------------------------------
% Toggles for submission
%--------------------------------------------------------------

%% Title page
%\anonymoustitlepage
\fulltitlepage

%% Comment out to double space footnotes
%\makeatletter
%\patchcmd{\@footnotetext}{\rule}{\normalsize \doublespacing\rule}{}{}
%\makeatother

%--------------------------------------------------------------
% Paper start
%--------------------------------------------------------------

\input{v1_paper/introduction}

%\input{v1_paper/exp_design}

\input{v1_paper/empirical_strategy}

%\input{v1_paper/data}

%\input{v1_paper/compliance}

\input{v1_paper/results}

\input{v1_paper/discussion}

\input{v1_paper/conclusion}


\clearpage
\bibliographystyle{apsr}
\typeout{}

\singlespacing

\bibliographystyle{apsr}
\bibliography{mercury}

\clearpage

\appendix

\setcounter{table}{0}
\setcounter{figure}{0}
\renewcommand{\thetable}{A\arabic{table}}
\renewcommand{\thefigure}{A\arabic{figure}}

\input{v1_paper/appendix_figures}

\clearpage
\setcounter{table}{0}
\setcounter{figure}{0}
\renewcommand{\thetable}{B\arabic{table}}
\renewcommand{\thefigure}{B\arabic{figure}}

\input{v1_paper/appendix}


\end{document}
